---
title: "test_for_new_package"
author: "zhang"
format: html
execute:
  echo: false
  output: false
editor: visual
---

## R library

```{r}
# | echo: false
library(dplyr)
library(tgcc)
```

## Source

```{r}
# | echo: false
Rcpp::sourceCpp("./src/main_init.cpp")
Rcpp::sourceCpp("./src/main_dp.cpp")
Rcpp::sourceCpp("./src/main_update.cpp")
source("./R/tgCC.R")
source("./R/utils.R")
```

## Prepare testing data set

```{r}
#| cache: true
#| message: false
#| echo: false
make.mixgaussian <- function(n) {
  n1 = round(n/3)
  n2 = n1
  n3 = n-n1-n2
  p = 2
  mean1 = t(matrix(c(1,2.5), nrow = p, ncol = n1))
  mean2 = t(matrix(c(2.5,-1.8), nrow = p, ncol = n2))
  mean3 = t(matrix(c(-2.5,-2), nrow = p, ncol = n3))
  noise1 = matrix(rnorm(n1*p, sd = 1), nrow = n1, ncol = p)
  noise2 = matrix(rnorm(n2*p, sd = 1), nrow = n2, ncol = p)
  noise3 = matrix(rnorm(n3*p, sd = 1), nrow = n3, ncol = p)
  data = rbind(noise1 + mean1, noise2 + mean2, noise3 + mean3)
  label = c(rep(1,n1), rep(2,n2), rep(3,n3))
  return(list(data = data, label = label))
}
```

## test tgCC

#### test tgcc()

#### test makeDendrogram()

```{r}
#| cache: false
#| message: false
set.seed(1)
dl <- make.mixgaussian(n = 400)
data <- dl$data
label <- dl$label
plot(data, col=label)

lamseq <- seq(20, 2000, length.out = 10000)
tgccFit <-
  tgCC(data = data, lambdaSeq = lamseq, depthThresh = 30)
tgcc:::makeDendrogram(tgccFit, label)
```

#### test tgccFit

```{r}
dim(tgccFit$theta[[100]])
all(tgccFit$data == data)
lapply(tgccFit$pointer, length) %>% unlist() %>% table

```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg== "Run Current Chunk")

#### test predLabel()

predLabel function

```{r}
predLabel <- clusterLabel(tgccFit, numClusters=3)
1-mclust::classError(label, predLabel)$errorRate
```

### test 2

```{r}
#| cache: true
#| message: false
set.seed(321)
dl <- make.mixgaussian(n = 1000)
data <- dl$data
label <- dl$label
plot(data, col=label)

lamseq <- seq(20, 50000, length.out = 10000)
tgccFit <- tgCC(data = data, lambdaSeq = lamseq, bandwidth = NULL, useNorm = TRUE, depthThresh = 100, probThresh = 0.3)
makeDendrogram(tgccFit, label) 
```

```{r}
predLabel <- clusterLabel(tgccFit, numClusters=3)
1-mclust::classError(label, predLabel)$errorRate
```

## Test Extension BiTgcc / SpTgcc

```{r}

```
